---
title: "Extra Credit: More JSON Practice"
author: "Fomba Kassoh"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Questions
1. What is the distribution of Nobel Laureates by continents and what is the gender distribution?
2. Which country “lost” the most nobel laureates (who were born there but received their Nobel prize as    a citizen of a different country
3. What categories were the nobel prices awarded and what is the average award by category?
4. Why is the award amount so different from the adjusted award amount?

# Load the libraries

```{r}
library(tidyverse)
library(httr)
library(jsonlite)

```


# Nobel Laureate data frame
```{r}
# Make the GET request
response <- GET("https://api.nobelprize.org/2.1/laureates")

# Check the status code to ensure the request was successful
if (status_code(response) == 200) {
  # Parse the JSON content
  json_content <- content(response, "text")
  json_data <- fromJSON(json_content)
} else {
  # Handle the case where the request was not successful
  cat("The request was not successful. Status code:", status_code(response))
}


 # Convert the data to a data frame
laureates_df <- as.data.frame(json_data$laureates)

# flatten the nested JSON
laureates_flat <- flatten(laureates_df)

 # Convert the flattened data to a data frame
laureates_df <- as.data.frame(laureates_flat)

# Display the first few rows of the dataframe
laureates_df
```
#1. What is the distribution of Nobel Laureates by continents and what is the gender distribution?

***answer***
Europe has the highest winners and there is only one female and is from Asia.

```{r}
laureates_df |> 
  group_by(continent = birth.place.continent.en, gender) |>
  count(gender) 

```


## 2. Which country “lost” the most nobel laureates (who were born there but received their Nobel prize       as a citizen of a different country

***answer***
Germany
```{r}
laureates_df |> 
  group_by('country of birth' = birth.place.country.en, 'country of citizenship' = birth.place.countryNow.en) |>
  summarise(n = n()) 

```



```{r}
# Load required libraries
library(httr)
library(jsonlite)

# Define the URL for the API endpoint
url <- "https://api.nobelprize.org/2.1/nobelPrizes?_ga=2.205366736.1362337552.1699405563-668968112.1699405563"

# Make the GET request to the API
response <- GET(url)

# Check if the request was successful
if (status_code(response) == 200) {
  # Parse the JSON content from the response
  content <- content(response, "text")
  json_data <- fromJSON(content)

# Convert the data to a data frame
nobelPrizes_df <- as.data.frame(json_data$nobelPrizes)

# flatten the nested JSON
nobelPrizes_flat <- flatten(nobelPrizes_df)

 # Convert the flattened data to a data frame
nobelPrizes_df <- as.data.frame(nobelPrizes_flat)

# Display the first few rows of the dataframe
nobelPrizes_df

} else {
  print(paste("Request failed with status", status_code(response)))
}

```

#3. What categories were the nobel prices awarded and what is the average award by category?

***answer***
The award categories are shown below and the average award is the same.

#4. What is the proportion of prize to adjusted prize. Why are the two so different?

***answer***
The proportion of prize to adjusted prize is about 1.58%. I do not know why they are so different.
```{r}
nobelPrizes_df |> 
  group_by(category.en) |>
  summarise('Average Award' = mean(prizeAmount), 'Award/Adjusted Award' = mean(prizeAmount)/mean(prizeAmountAdjusted))

```
