---
title: "Final Project"
author: "Fomba Kassoh & Souleymane Doumbia"
date: "2023-12-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load necessary libraries
library(readr)
library(tidyr)
library(dplyr)
library(stringr)

# Load the dataset with specified column types
audible_books <- read_csv("https://raw.githubusercontent.com/hawa1983/DATA607/main/audible_books.csv", 
  col_types = cols(
    title = col_character(),
    subtitle = col_character(),
    authors = col_character(),
    narrators = col_character(),
    series = col_character(),
    length = col_character(),
    release_date = col_character(),
    language = col_character(),
    rating = col_character(),
    no_of_ratings = col_character(),
    regular_price = col_character(),
    sales_price = col_logical(),
    category = col_logical(),
    genres = col_character(),
    url = col_character()
))
```

# Data Tydying

## Parsing and Cleaning 'authors', 'narrators', and 'genres' Fields
These fields contain data in a list-like format (e.g., ['Meghan Quinn'], ['Connor Crais', 'Erin Mallon', 'Teddy Hamilton']). For easier analysis, these could be split into separate columns or transformed into a more consistent format.

```{r}
# Trim leading and trailing whitespaces
audible_books$authors <- trimws(audible_books$authors)
audible_books$narrators <- trimws(audible_books$narrators)

# Define a function to clean and split the data
clean_and_split <- function(column) {
  # Remove brackets, different types of quotes, and trim again
  cleaned_column <- gsub("[\\[\\]']", "", column)
  cleaned_column <- trimws(cleaned_column)
  
  # Split the column into separate columns
  separated_columns <- str_split_fixed(cleaned_column, ",\\s*", n = max(str_count(cleaned_column, ",") + 1))
  
  return(separated_columns)
}

# Apply the function to authors and narrators
author_columns <- clean_and_split(audible_books$authors)
narrator_columns <- clean_and_split(audible_books$narrators)

# Convert the matrices to data frames
author_df <- as.data.frame(author_columns, stringsAsFactors = FALSE)
narrator_df <- as.data.frame(narrator_columns, stringsAsFactors = FALSE)

# Add new columns to the original dataframe
audible_books <- cbind(audible_books, author_df, narrator_df)

# Optionally, rename the new columns for clarity
colnames(audible_books)[(ncol(audible_books)-ncol(author_df)-ncol(narrator_df)+1):ncol(audible_books)] <- 
    c(paste0("author_", seq_len(ncol(author_df))), paste0("narrator_", seq_len(ncol(narrator_df))))

# View the modified dataframe
head(audible_books)
```

## Extracting Numeric Data from 'length', 'rating', and 'no_of_ratings'


## Handling Missing Data

## Standardizing 'release_date' and 'language': 

## Formatting Price Fields

## Addressing Empty 'genres' Field

## Consistency in Series Information

## URLs Verification